Lexical Richness as a Lens: Exploring the Influence of Social Class on Authors' Writings

### 2024-03-16 paper/paper.qmd
updating current work process: creating figures for result and data

cleaned_data <- read.csv(here::here("data/analysis_data/cttr_all.csv"))

cleaned_data |>
  select(author, title, word_count, types) |>
  slice(1:10) |>
  kable(
    col.names = c("author", "title", "word count", "unique word count"),
    digits = 1,
    booktabs = TRUE
  )
```
@tbl-authors-cttr
# TODO: Explain

@@

## Author's average word counts distribution
```{r}
#| label: Authors-Word-Count-and-CTTR-Distribution
#| fig-cap: Change in Birth Rates by State, 2004–2008 to 2015–2019
#| echo: false

>>>>

cttr_all <- read.csv(here::here("data/analysis_data/cttr_all.csv"))

cttr_all |>
  select(author, title, word_count, types) |>
  slice(1:10) |>
  kable(
    col.names = c("author", "title", "word count", "unique word count"),
    digits = 1,
    booktabs = TRUE
  )
```

@tbl-authors-cttr

## Author's average word counts distribution
```{r}
#| label: Authors-Word-Count-Distribution
#| fig-cap: "Word Count Comparison by Authors"
#| echo: false

cttr_all <- read.csv(here::here("data/analysis_data/cttr_all.csv"))

ggplot(cttr_all, aes(x = title, y = word_count, color = author)) +
  geom_line(linewidth=1) +
  labs(x = "Title",
       y = "Word Count") +
  theme(panel.background = element_rect(fill = "white"),
              panel.grid.major = element_line(colour = "grey"),
              plot.title = element_text(color = "black", size = 14, face = "bold"),
              axis.title = element_text(color = "black"))
```
# TODO: Explain

@@
